---
params:
  CPT: 123456
  printcode: FALSE
  date: 12/12/12
  profile: Male, Acites, Current Smoker
  destination_home: 95
  destination_readmit: 5
  destination_death: 1
  plot_func: NULL
  event_data: NULL
  plot1 : NULL
  top_arrow : plot1.jpg
  middle_arrow: plot1.jpg
  bot_arrow: plot1.jpg
  complications_background : images/total.jpg
  bottom_complications_background : images/bottom.jpg

output: 
  pdf_document:
    fig_caption: false
    keep_tex: yes
  
title: ""
sansfont: Calibri Light
fontsize: 11pt
classoption: landscape
header-includes:
  - \usepackage{floatrow}
  - \usepackage{caption}
  - \usepackage{subcaption}
  - \usepackage{background}
  - \usepackage{titling}
  - \usepackage{xcolor}
  - \usepackage{graphicx}
  - \usepackage{tikz}
  - \usepackage[most]{tcolorbox}
  - \usetikzlibrary{calc}
  - \usepackage{caption}
  - \usepackage{background}
  - \usepackage{subcaption}
  - \usepackage[absolute,overlay]{textpos}
  - \pretitle{\begin{flushleft}}
  - \posttitle{\end{flushleft}}
  - \definecolor{amethyst}{RGB}{123, 186, 233}
  - \color{black}
  - \geometry{top=0.75in,left=0.80in,bottom=0.75in,right=0.80in}
---

```{r, setup, include=FALSE}
# set this option in the first code chunk in the document
library(ggplot2)
library(formattable)
```

\thispagestyle{empty}

\begin{tikzpicture}[overlay, remember picture]
\node[anchor=west, %anchor is upper left corner of the graphic
      xshift=0cm, %shifting around
      yshift=0cm] 
     at (current page.west) %left upper corner of the page
     {\includegraphics[width=\paperwidth,height=\paperheight]{"New Images/Background_1.png"}}; 
\end{tikzpicture}

\begin{tikzpicture}[overlay, remember picture]
\node[anchor=west, %anchor is upper left corner of the graphic
      xshift=0cm, %shifting around
      yshift=0cm] 
     at (current page.west) %left upper corner of the page
     {\includegraphics[width=\paperwidth,height=\paperheight]{`r params$bot_arrow`}}; 
\end{tikzpicture}

\begin{tikzpicture}[overlay, remember picture]
\node[anchor=west, %anchor is upper left corner of the graphic
      xshift=0cm, %shifting around
      yshift=0cm] 
     at (current page.west) %left upper corner of the page
     {\includegraphics[width=\paperwidth,height=\paperheight]{`r params$middle_arrow`}}; 
\end{tikzpicture}


\begin{tikzpicture}[overlay, remember picture]
\node[anchor=west, %anchor is upper left corner of the graphic
      xshift=0cm, %shifting around
      yshift=0cm] 
     at (current page.west) %left upper corner of the page
     {\includegraphics[width=\paperwidth,height=\paperheight]{`r params$top_arrow`}}; 
\end{tikzpicture}



\begin{tikzpicture}[overlay, remember picture]
\node[anchor=west, %anchor is upper left corner of the graphic
      xshift=0cm, %shifting around
      yshift=0cm] 
     at (current page.west) %left upper corner of the page
     {\includegraphics[width=\paperwidth,height=\paperheight]{"New Images/background_3.png"}}; 
\end{tikzpicture}




\begin{textblock*}{5cm}(3.9cm,9.4cm) % {block width} (coords) 
    \centerline{\small{`r params$event_data[["V1"]][1]`}}
\end{textblock*}

\begin{textblock*}{5cm}(3.9cm,9.9cm) % {block width} (coords) 
    \small \centerline{\textit{`r params$event_data[["V2"]][1]`}}
\end{textblock*}

\begin{textblock*}{5cm}(3.9cm,10.3cm) % {block width} (coords) 
    \centerline{\textbf{`r paste(sprintf("%.2f",params$event_data[["V3"]][1]), '\\%', sep = "")`}}
\end{textblock*}



\begin{textblock*}{5cm}(9.4cm,9.4cm) % {block width} (coords) 
    \centerline{\small{`r params$event_data[["V1"]][2]`}}
\end{textblock*}

\begin{textblock*}{5cm}(9.4cm,9.9cm) % {block width} (coords) 
    \small \centerline{\textit{`r params$event_data[["V2"]][2]`}}
\end{textblock*}

\begin{textblock*}{5cm}(9.4cm,10.3cm) % {block width} (coords) 
    \centerline{\textbf{`r paste(sprintf("%.2f",params$event_data[["V3"]][2]), '\\%', sep = "")`}}
\end{textblock*}



\begin{textblock*}{5cm}(14.9cm,9.4cm) % {block width} (coords) 
    \centerline{\small{`r params$event_data[["V1"]][3]`}}
\end{textblock*}

\begin{textblock*}{5cm}(14.9cm,9.9cm) % {block width} (coords) 
    \small \centerline{\textit{`r params$event_data[["V2"]][3]`}}
\end{textblock*}

\begin{textblock*}{5cm}(14.9cm,10.3cm) % {block width} (coords) 
    \centerline{\textbf{`r paste(sprintf("%.2f",params$event_data[["V3"]][3]), '\\%', sep = "")`}}
\end{textblock*}




\begin{textblock*}{5cm}(3.9cm,17.55cm) % {block width} (coords) 
    \centerline{\small{`r params$event_data[["V1"]][4]`}}
\end{textblock*}

\begin{textblock*}{5cm}(3.9cm,18.05cm) % {block width} (coords) 
    \small \centerline{\textit{`r params$event_data[["V2"]][4]`}}
\end{textblock*}

\begin{textblock*}{5cm}(3.9cm,18.4cm) % {block width} (coords) 
    \centerline{\textbf{`r paste(sprintf("%.2f",params$event_data[["V3"]][4]), '\\%', sep = "")`}}
\end{textblock*}



\begin{textblock*}{5cm}(9.4cm,17.55cm) % {block width} (coords) 
    \centerline{\small{`r params$event_data[["V1"]][5]`}}
\end{textblock*}

\begin{textblock*}{5cm}(9.4cm,18.05cm) % {block width} (coords) 
    \small \centerline{\textit{`r params$event_data[["V2"]][5]`}}
\end{textblock*}

\begin{textblock*}{5cm}(9.4cm,18.4cm) % {block width} (coords) 
    \centerline{\textbf{`r paste(sprintf("%.2f",params$event_data[["V3"]][5]), '\\%', sep = "")`}}
\end{textblock*}



\begin{textblock*}{5cm}(14.9cm,17.55cm) % {block width} (coords) 
    \centerline{\small{`r params$event_data[["V1"]][6]`}}
\end{textblock*}

\begin{textblock*}{5cm}(14.9cm,18.05cm) % {block width} (coords) 
    \small \centerline{\textit{`r params$event_data[["V2"]][6]`}}
\end{textblock*}

\begin{textblock*}{5cm}(14.9cm,18.4cm) % {block width} (coords) 
    \centerline{\textbf{`r paste(sprintf("%.2f",params$event_data[["V3"]][6]), '\\%', sep = "")`}}
\end{textblock*}


\begin{textblock*}{3cm}(24.1cm,8.2cm) % {block width} (coords) 
  \huge \textcolor{black}{\textbf{`r sprintf("%.2f",params$destination_home)`} \huge \%}
\end{textblock*}

\begin{textblock*}{3cm}(24.1cm,12.1cm) % {block width} (coords) 
  \huge \textcolor{black}{\textbf{`r sprintf("%.2f",params$destination_readmit)`} \huge \%}
\end{textblock*}

\begin{textblock*}{3cm}(24.1cm,16cm) % {block width} (coords) 
  \huge \textcolor{black}{\textbf{`r sprintf("%.2f",params$destination_death)`} \huge \%}
\end{textblock*}




\vspace{2.75em}

\begin{figure}
 \hspace{-4.24cm}
 \begin{subfloatrow}%

\ffigbox[20cm][]{%
 \begin{subfloatrow}[3]%
 \ffigbox[5.3cm][]{%
```{r,fig.align = "center", fig.width=0.85, fig.height=0.85, echo = F}
    params$plot_func(params$event_data[["V3"]][1])
```
    }{{}}

    \ffigbox[5cm][]{%
```{r,fig.align = "center", fig.width=0.85, fig.height=0.85, echo = F}
    params$plot_func(params$event_data[["V3"]][2])
```
    }{{}}
    
    \ffigbox[5.2cm][]{%
```{r,fig.align = "center", fig.width=0.85, fig.height=0.85, echo = F}
    params$plot_func(params$event_data[["V3"]][3])
```
    }{{}}
      
    \end{subfloatrow}
  }{
   
  }
  \end{subfloatrow}
\end{figure}

\vspace{4.48cm}

\begin{figure}
 \hspace{-4.24cm}
 \begin{subfloatrow}%

\ffigbox[20cm][]{%
 \begin{subfloatrow}[3]%
 \ffigbox[5.3cm][]{%
```{r,fig.align = "center", fig.width=0.85, fig.height=0.85, echo = F}
    params$plot_func(params$event_data[["V3"]][4])
```
    }{{}}

    \ffigbox[5cm][]{%
```{r,fig.align = "center", fig.width=0.85, fig.height=0.85, echo = F}
    params$plot_func(params$event_data[["V3"]][5])
```
    }{{}}
    
    \ffigbox[5.2cm][]{%
```{r,fig.align = "center", fig.width=0.85, fig.height=0.85, echo = F}
    params$plot_func(params$event_data[["V3"]][6])
```
    }{{}}
      
    \end{subfloatrow}
  }{
   
  }
  \end{subfloatrow}
\end{figure}

\begin{flushright}
\vspace{-16.5cm} \hspace{18cm} \normalsize Date Calculated:

\vspace{-0.25 cm} \hspace{18cm} \normalsize \textbf{`r params$date`}

\vspace{-0.2cm} \hspace{18cm} \normalsize For the following procedure

\vspace{-0.2cm} \hspace{18cm} \small \textbf{`r params$CPT`}

\vspace{-0.2cm} \hspace{18cm} \normalsize With the following profile:

\vspace{-0.2cm} \hspace{18cm} \small \textbf{`r params$profile`}
\end{flushright}
